Location and Scale-Invariant Power Transformations for Transforming Data to

### 2025-03-09 manuscript_rmarkdown/manuscript.Rmd
Update text for new ML experiments.

* very easy: $\text{AUC} \geq 0.90$ or $\text{RRSE} \leq 0.10$ (59 datasets)
* easy: $0.90 > \text{AUC} \geq 0.80$ or $0.30 \geq \text{RRSE} > 0.10$ (40 datasets)
* intermediate: $0.80 > \text{AUC} \geq 0.70$ or $0.60 \geq \text{RRSE} > 0.30$ (50 datasets)
* difficult: $0.70 > \text{AUC} \geq 0.60$ or $0.80 \geq \text{RRSE} > 0.60$ (32 datasets)
* very difficult: $0.60 > \text{AUC} \geq 0.50$ or $1.00 \geq \text{RRSE} > 0.80$ (49 datasets)
* unsolvable: $\text{AUC} < 0.50$ or $\text{RRSE} > 1.00$ (1 dataset)

@@

Considering single process parameters, the choice of learner (Friedman test: $p < 10^{-8})$), normalisation method (Wilcoxon signed rank test: $p < 10^{-5}$), and transformation method $p = 0.006$, all had a significant impact (at significance level $p = 0.05$).

@@

Location- and scale-invariant power transformations were implemented in the `power.transform` package for R, which is available from [GitHub](https://github.com/oncoray/power.transform) and the [CRAN repository](https://cran.r-project.org/package=power.transform). The manuscript was created using R Markdown and is likewise available from the `power.transform` GitHub repository. Data and results for the machine learning experiment are separately available from [Zenodo](https://doi.org/10.5281/zenodo.13736671).

>>>>

* very easy: $\text{AUC} \geq 0.90$ or $\text{RRSE} \leq 0.10$ (57 datasets)
* easy: $0.90 > \text{AUC} \geq 0.80$ or $0.30 \geq \text{RRSE} > 0.10$ (40 datasets)
* intermediate: $0.80 > \text{AUC} \geq 0.70$ or $0.60 \geq \text{RRSE} > 0.30$ (52 datasets)
* difficult: $0.70 > \text{AUC} \geq 0.60$ or $0.80 \geq \text{RRSE} > 0.60$ (33 datasets)
* very difficult: $0.60 > \text{AUC} \geq 0.50$ or $1.00 \geq \text{RRSE} > 0.80$ (48 datasets)
* unsolvable: $\text{AUC} < 0.50$ or $\text{RRSE} > 1.00$ (1 dataset)

@@

Considering single process parameters, the choice of learner (Friedman test: $p < 10^{-8})$), normalisation method (Wilcoxon signed rank test: $p < 10^{-8}$), and transformation method $p = 0.007$, all had a significant impact (at significance level $p = 0.05$).

@@

Location- and scale-invariant power transformations were implemented in the `power.transform` package for R, which is available from [GitHub](https://github.com/oncoray/power.transform) and the [CRAN repository](https://cran.r-project.org/package=power.transform). The manuscript was created using R Markdown and is likewise available from the `power.transform` GitHub repository. Data and results for the machine learning experiment are separately available from [Zenodo](https://doi.org/10.5281/zenodo.14986689).
